
The process of choosing the most optimal branching literal is a NP-hard problem, hence it is not possible to 
just calculate the best solution. So instead it is necesairy to use a heuristic.
These heuristics calculate a subset of the complete solution and base their descission on this subset.

In order to solve a SAT problem as efficient as possible the search space must be reduced as much as possible.
This reduction is achieved by taking symmetries into account while evaluating a SAT instance.
To reduce the search space as much as possible, heuristics must optimize the amount of active symmetries as observed by~\cite{devriendt2012symmetry}.

The authors of~\cite{devriendt2012symmetry} suggest the possibility of optimizing the solver by
branching on literals that optimize the number of symmetries that are (weakly) active.
They took a step in that direction by lowering the position of \emph{inverting} literals $v$ on the variable heap for
every symmetry $\sigma$ such that $\sigma(v) = \neg v$.
Because choosing such variables would cause these symmetries to become permanently weakly inactive.
Using this heuristic they showed a considerable performance boost, which prompted our research.

In this section we consider several implementations of this heuristic: promoting choice literals
that keep or make symmetries weakly active.
In the next section we compare the performance of these implementations and discuss their
applicability.

\subsection{Literal Lookahead}
	To also consider the effects of choice literals on the activity of symmetries further,
	we propose a heuristic \emph{literal lookahead} that checks if symmetries are made weakly inactive by a choice literal.
	Given the definition of weak activity in \cite{devriendt2012symmetry} we can define \cref{cor:makes_inactive}.\\

	\begin{corollary}
		\label{cor:makes_inactive}
		Given a symmetry $\sigma$ and a choice literal $l$,
		$\sigma$ is made weakly inactive by choosing $l$ iff
		$\sigma$ is weakly active, and $\sigma(l) \notin \alpha$.
		Where $(\alpha,\delta,\textit{expl})$ is the solver state \textbf{after} unit propagation of $l$. \todo{Can we express this differently?}
	\end{corollary}

	In order to determine the activity of symmetries exactly after choosing a literal,
	it is necessary to perform the unit propagation step under the assumption that the literal is chosen.
	Performing a lookahead is an expensive operation as it requires the solver to perform half an
	iteration and backtrack.

	In fact, it is necessary to perform $|L|$ lookaheads, where $L = \bar{\Sigma}(T)$ is the set of literals.
	And each lookahead consists of a unit propagation and a symmetry propagation step.
	The unit propagation phase iterates through all clauses in a time complexity of $O(|T|)$.
	This occurs in the worst case $O(|L|)$ times,
	once for each literal if all literals are assigned in in this unit propagation phase.
	Then comes the symmetry propagation phase, which iterates through all symmetries in $O(|\mathcal{S}|)$.
	If the symmetry propagation phase found a (weakly) active symmetry and propagated that,
	the propagation will repeat.
	In total this process can repeat more than $O(|L|)$ times,
	so the total worst-case complexity of the lookahead can be simplified to $O(|L|(|T| + |\mathcal{S}|))$.

	It is possible to reduce the cost of the lookahead, by only considering $m$ variables on
	the top of the variable heap.
	By doing so, the heuristic would honor the order of the variable heap.
	This implies that it honors other heuristics that promote variables through variable activity,
	such as the heuristic suggested by \cite{devriendt2012symmetry} and the heuristics that were
	implemented in the core of MiniSat by \cite{een2004extensible}.\todo{background on variable
	activity}

	It is thus not feasible in general to perform this procedure for every undecided variable and
	select the optimal one.
	Several alternative approaches can be considered.
	An obvious choice is to perform a lookahead on the choice variable $v$ that the solver
	selects (based on the variable heap and activity\todo{ref}) to determine the
	preferred assignment ($v$ or $\neg v$).

	Additionally, one could perform this lookahead for the $n$ most eligible variables
	and select the one that makes the least symmetries inactive.
	By combining this with other heuristics on selecting the most eligible variables,
	a much faster runtime may be achieved.

	\subsubsection{Working around the lookahead}
		It is also possible to approximate the amount of symmetries made inactive under the
		assignment that the propagation of $l$ will yield.
		Instead of propagating, we can look at the number of symmetries made inactive by $l$
		under the current assignment, that is: consider a symmetry $\sigma$ as
		made inactive by $l$ if it is weakly active under the current assignment $\alpha$ and
		$\sigma(l) \notin \alpha$.
		Note that this is a rough approximation only, as these symmetries could be made active by
		unit propagation after choosing $l$.

\subsection{Symmetry Counting}

	Choosing a literal that occurs in a symmetry, increases the activity of that symmetry.
	Following the line of thought of attempting to keep as much symmetries active as possible,
	one could attempt to promote literals that appear in many symmetries.

	A possible implementation of this heuristic would increase the activity for every variable in
	every symmetry, when the symmetries are inputted into the solver.
	This implementation would only cost a polynomial amount of runtime, at the initialization of the
	solver and can be combined with any other heuristic that honors the order of the variable heap.

\subsection{Symmetry Usage}
	Symmetry Usage is a dynamical symmetry breaking heuristic
	which takes into account the number of times a symmetry has previously been used in the solver tree.
	If a symmetry is used often when solving the tree, we suppose that it is more important than other symmetries.

	We can implement the same approach as in the symmetry counting heuristic: when a symmetry is
	used to propagate literals, the variables that are part of that symmetry are bumped up the
	variable heap.

	% -- old implementation
	%When choosing a literal, those that are used in commonly used symmetries, are chosen first, such
	%that these \emph{important symmetries} will become more strongly active.

	%The implementation is a simple counter that is increased by 1 for each usage of the symmetry.
	%The main runtime drawback of this heuristic, is looping through all symmetries a literal is involved in.
	%We do this for each literal, which has a runtime of $O(|L|)$.
	%The other additional operations are of a constant time complexity $O(1)$, thus the additional overhead is $O(s|L|)$,
	%where $s$ is the maximum number of symmetries a literal is involved in.

