The implementation of the alternative heuristics is based on the improvements
made by~\cite{devriendt2012symmetry} based on the MiniSAT SAT-solver.
In order to ease the testing procedure and overall usage of the solver, all heuristics
are implemented within the same program. One may choose one or multiple heuristics
by using command line parameters. Because of this feature it is possible to combine
multiple heuristics into a new heuristic.
While benchmarking we disabled the builtin heuristic that randomly chooses a literal from the heap,
such that our results are fully deterministic.
Further combinations of heuristics are not tested because this falls outside the scope
of this research.

We will analyze the results for each of the heuristics seperately and discuss for each of them both
hypothesis as formulated in section \ref{sec:Introduction}.
Beforehand we discuss some results that are observed for each of the measured heuristics.

\subsection{Generic Results}
	Firstly, it is observed that $SP^{REG}$ and $SP^{OPT}$ perform equally on all measured sets,
	except Urquhart.
	This conforms to our expectations, as the only difference between these implementations is the
	optimizing heuristic for inverting symmetries, and only the Urquhart set contains inverting
	symmetries in our selection of benchmarks.

	It is observed in the activity data that none of implementations, including $SP^{OPT}$,
	succeeds in increasing the number of active symmetries in the CHNL benchmark suite.

	The same is true for the Urquhart benchmarks.
	This however was to be expected, as it only contains inverting symmetries.
	The searcher therefor picks a branch literal (that is expected to keep more symmetries active),
	but during symmetry propagation, the weakly active symmetry would be made permanently inactive
	because it contains literals that invert under the symmetry.

	One might expect that SA would perform better under these circumstances.
	However, our implementation only performs \emph{unit propagation} during the lookahead, such
	that inverting symmetries are counted as active during the lookahead.

\subsection{SA Heuristic}
	From a theoretical perspective, SA was expected to have the most impact on the number of active
	symmetries during search, as it optimizes is very directly using a one iteration lookahead.
	This is reflected in the measured active symmetries.
	From all four heuristics, the SA heuristic is the one that performs best on this metric.

	The most prominent result is that it performs better (on the activity metric) than $SP^{OPT}$ in
	all but two battleship instances.
	Additionally, it keeps more symmetries active in the part of the shuffled pigeonhole benchmarks
	that did not time-out.

\subsection{SU Heuristic}
	The symmetry usage statistic is performing very badl
