\input{../header}

\title{Symmetry Breaking}

\begin{document}
	\maketitle
	
	%\tableofcontents
	\listoftodos

	\begin{abstract}
		\todoi{Abstract}
	\end{abstract}
	
	\section{Introduction} \label{sec:Introduction}
		Symmetry breaking has become an interesting method for increasing the solving speed of certain Conjunctive Normal Form (CNF) Satisfiability (SAT) problems.
		This is typically done by adding Symmetry Breaking Predicates (SBPs) to the SAT instance~\cite{sakallah2009symmetry},
		resulting in a simpler search space.
		There are generally speaking two types of symmetry breaking: Static symmetry breaking and dynamic symmetry breaking.
		While static symmetry breaking has become more popular\todo{Need ref}, we will investigate the pros and cons of dynamic symmetry breaking.
		
		We will also investigate what classes of problems symmetry breaking can be applied to and what the effective speed-up pertains.
		For symmetry breaking to be applied effectively the given problem has to exert symmetrical properties,
		i.e.\ some search tree is virtually identical to another.
		Symmetry breaking has been shown to provide significant speed-ups~\cite{darga2004exploiting,aloul2003solving},
		and do not slow down the algorithm when no obvious symmetries are present.
		
		Then we will investigate these claims by applying a given symmetry breaking algorithm to a problem, modifying it and empirically judge its effectiveness. \todoi{Introduction to our SB algorithm}
		
	\section{Background} \label{sec:Background}
		To prevent a SAT solver from researching a symmetrical search tree, that was already solved before,
		Symmetry Breaking Predicates can be added to the SAT instance~\cite{sakallah2009symmetry}.		
		SBPs can also be applied partially to the symmetry group, called \textit{partial symmetry breaking}~\cite{sakallah2009symmetry}.
		Because \textit{full symmetry breaking} sometimes costs a lot of time, most symmetrical search spaces can be blocked by using a subset of the full SBP.
		There has been more research on the efficiency of SBPs, such as \cite{aloul2006efficient}\todo{More refs}.
		
		\todoi{Conflict-Driven symmetry breaking}
		
		\subsection{Static Symmetry Breaking}
			Static symmetry breaking algorithms modify the input of the SAT solver, but do not adjust the solver itself~\cite{sakallah2009symmetry}.
			
		\subsection{Dynamic Symmetry Breaking}
			Dynamic symmetry breaking algorithms modify the SAT solver to search for local symmetries during runtime.
			Contributions to dynamic symmetry breaking have not been numerous in SAT such as \cite{sabharwal2005symchaff},
			where Constraint Satisfaction Problems (CSP) have looked more research in the matter. 	

	\nocite{*} %Show everything in bib
	\bibliographystyle{IEEEtran}
	\bibliography{../bibliography}
\end{document}
